### 2020-03-11 tex/threat-network-model.tex
Fix minor typos. Added some initial comments.

\section{Threat and Network Models}
\label{threat-network-model}
This section describes a modification for the network model of NuCypher 
KMS required by the proposed confirm service activity solutions, in 
addition to the threat model we adopt in this document.

@@

The following approach can be used here; given that Umbral already requires Bob to 
have a key pair, this pair can be used for signing and verifying the signed requests. 
This also means that Ursula should be aware  the secret key can be used for the 
signing the requests and the public 
key should be known to Ursula to verify the signatures.

>>>>

\section{Threat and Network Models}
\label{threat-network-model}
This section describes a modification for the network model of NuCypher 
required by the proposed confirm service activity solutions, in 
addition to the threat model we adopt in this document.

@@

\david{NuCrypher currently supports this by allowing Bob to include a blockhash,
although it's not being used for the moment.}

The following approach can be used here; given that Umbral already requires Bob to 
have a key pair, this pair can be used for signing and verifying the signed requests. 
This also means that Ursula should be aware the secret key can be used for 
signing the requests and the public 
key should be known to Ursula to verify the signatures.

\david{Reusing the same keypair for encryption and signing may introduce some key management problems. Is it possible to find a solution that supports separate keypairs?}
